Robotic Manipulator Path Planning Utilizing Interpolated 3D Voxel-Based Obstacle Avoidance Method

### 2023-11-13 Articles/Article 1/main.tex
more planning

%opening
\title{\comment{3D Voxel Grid Based Path Planning for Robotic Manipulators using Matrix Multiplication Technique}{Alternatives:\\ - Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based Robotic Manipulator Path Planning \\ - Robotic Manipulator Path Planning Optimization Using Matrix-Derived Repulsive Fields Based on 3D Voxel Grid}}

@@

\add{
	- method was inspired by Khatib APF (however, it evolved into a different method) \\
	- different existing APF manipulator implementation articles \\
	- VFH \\
}

@@

\add{
	- optimization algorithm \\
	- robot kinematics (include the exact-reduced method) \\
	- primary task of distance goal \\
	- secondary task of repulsive field \\
	- task slowdown option \\
	- secondary task of manipulation measure \\	
}

@@

\add{	
	- repulsive field calculation - matrix "convolution" method \\
	- matrix size and shape selection \\
	- PLOT: (ERK) kernel graphics \\
	- PLOT: (ERK) linear kernel graphics \\
	- PLOT: kernel field shape 	\\
	- interpolation of the repulsive field \\
}

>>>>

%opening
\title{\comment{3D Voxel Grid Based Path Planning for Robotic Manipulators using Matrix Multiplication Technique}{Alternatives:\\ - Efficient distance calculation / Efficient repulsive field calculation technique \\   - Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based Robotic Manipulator Path Planning \\ - Robotic Manipulator Path Planning Optimization Using Matrix-Derived Repulsive Fields Based on 3D Voxel Grid}}

@@

\add{
	- PRESENT DISTANCE CALCULATION FOR MANIPULATORS (sensors, lidar, ir, bounding boxes) \\
	- PRESENT PATH PLANNING METHODS FOR MANIPULATOR (optimization, sampling, biological, learning) \\
	- similar to Distance Transform (a kind of inverted distance transform) \\
	- method was inspired by Khatib APF (however, it evolved into a different method) \\
	- different existing APF manipulator implementation articles \\
	- VFH \\
}

@@

\add{
	- optimization algorithm \\
	- robot kinematics (include the exact-reduced method) \\
	- primary task of distance goal \\
	- secondary task of repulsive field \\
	- damped least squares \\
	- task slowdown option \\
	- secondary task of manipulation measure \\	
}

@@

\add{	
	- object detection is done in task domain and not c-space (more logical) \\
	- repulsive field calculation - matrix "convolution" method \\
	- matrix size and shape selection \\
	- equation for repulsive kernel values (non-linear) \\
	- PLOT: (ERK) kernel graphics \\
	- PLOT: (ERK) linear kernel graphics \\
	- PLOT: kernel field shape 	\\
	- interpolation of the repulsive field \\
	- what if there are obstacles behind wall (usually not the case, depth sensors show only thin walls, some noise doesnt matter, non-linear kernel, possible additional pre-convolution to convert obstacle grid to edges) \\
	- effecient calculation in dinamic environments, lacking prediction capabilities (MPC) \\
}

\subsubsection{Kernel Selection}

\subsubsection{Interpolation}
